Stability of flower visitation rate over time is driven by asynchrony of pollinator abundances but does not determine the stability of plant reproductive success.

### 2023-02-13 Manuscript/Manuscript.Rmd
edit discussion

Temporal stability is defined as the capacity of an ecosystem to dampen environmental perturbations over time while retaining ecological functions of interest [@Ives2007; @Pimm1984].
The temporal stability of community can be influenced by the diversity of species present and the asynchrony on the species abundance fluctuations.
A higher number of species might stabilize community level functions by increasing the range of species level potential responses to environmental changes (i.e. the portfolio effect) [@McCann2000; @Tilman2006; @Hector2010; @Xu2021], although non-significant relationships between diversity and stability have also been observed [@Hooper2005; @VanderPlas2019].
The degree of asynchrony in species abundance fluctuations is also a stabilizing mechanisms.
In this sense, higher levels of asynchrony stabilize the community [@Ruijven2007; @Bluthgen2016; @Craven2018]. Species asynchrony has been found to be a key factor driving positive relationships between diversity and stability [@Loreau2008;@Xu2015] or even that stability is often more strongly associated with the degree of asynchrony across species than with species richness [@Bluthgen2016;@Huang2020]. Other studies have indicated that temporal stability of the dominant species or asynchrony among these dominant species is important in maintaining the stability of ecosystems [@Sasaki2011; @Valencia2020]. While community temporal stability should be related to the stability of ecosystem functions and services provided by such community, there is limited evidence linking both processes on multitrophic systems.

@@

While drivers of temporal stability have been well study in plant communities [@Ruijven2007; @Gross2014; @Craven2018; @Leps2018; @Sasaki2019; @Valencia2020; @Kigel2021], relatively few studies have evaluated how this same drivers can affect community stability in mobile organisms such as pollinators [@Ebeling2008; @Senapathi2021; @Lazaro2022].
A first clear outcome of our analysis is that asynchrony of species abundances is a key driver of visitation rate stability.
This stability-asynchrony relationship has been found by different theoretical and empirical studies [@DeMazancourt2013; @Bluthgen2016; @Leps2018; @Sasaki2019; @Valencia2020; @Kigel2021].
For example, Lázaro et al.(2022) also found for plants, pollinators and their interactions that more asynchronous communities being more temporal stable.
[The fact that species asynchrony increases the temporal stability of the visitation rate is likely because a decrease in the abundance of one pollinator species is compensated by an increase of the abundance of another.](escribir%20mejor%20la%20frase)
[mirate los appaers de Winfree sobre esto que lo explica muy bien y explica mecanismos] On the other hand, species richness is considered one of the strongest drivers of community stability [in plants?]
(Tilman et al., 2006; de Mazancourt et al., 2013; Hallett et al., 2014), although Valencia et al.(2020) have reported that this relation is not nearly as strong [where?].
Pollinator studies have observed a positive relationship between richness and stability of what?
in crops??
(Ebeling et al 2008; Senapathi et al 2021), however, our results show that richness was positively associated with asynchrony, which might positively affect the stability of visitation rate, but indirectly.
[This most likely reflects niche variation among species that affect their relative performance over time in a temporally variable environment (Yachi & Loreau,1999; Gross et al., 2014; Craven et al 2018).](??)

Despite the stability is crucial to the sustainability of ecosystem functions, relatively few studies have evaluated the stability of the pollinator visits frequency on pollination services, and those who did used agricultural systems [right?]
(Garibaldi et al. 2011, Lázaro and Alomar 2019, Hünicken et al 2021, Bishop et al 2022).The majority of these studies were focused on crops, however, to our knowledge, how the stability of pollinator community affect to the reproductive success of the wild plant community remaining largely unknown.
In pollinator-dependent crops have been observed a greater yield stability with the pollinator diversity and the stability of visitation rate (Garibaldi et al. 2011, Hünicken et al 2021), however in our study system (wild plants), we did not find this relationship or even observed a negative relationship between seed number stability and visitation rate stability.

>>>>

Temporal stability is defined as the capacity of an ecosystem to dampen environmental perturbations over time while retaining ecological functions of interest [@Ives2007; @Pimm1984].
The temporal stability of community can be influenced by the diversity of species present and the asynchrony on the species abundance fluctuations.
A higher number of species might stabilize community level functions by increasing the range of species level potential responses to environmental changes (i.e. the portfolio effect) [@McCann2000; @Tilman2006; @Hector2010; @Xu2021], although non-significant relationships between diversity and stability have also been observed [@Hooper2005; @VanderPlas2019].
Species asynchrony represents the intrinsic differences in species response to disturbances and natural fluctuations [@Loreau2013] which has been suggested as a key driver for community temporal stability [@Loreau2008].
In this sense, higher levels of asynchrony stabilize the community [@Ruijven2007; @Bluthgen2016; @Craven2018]. Species asynchrony has been found to be a factor driving positive relationships between diversity and stability [@Loreau2008;@Xu2015] or even that stability is often more strongly associated with the degree of asynchrony across species than with species richness [@Bluthgen2016;@Huang2020]. Other studies have indicated that temporal stability of the dominant species or asynchrony among these dominant species is important in maintaining the stability of ecosystems [@Sasaki2011; @Valencia2020]. While community temporal stability should be related to the stability of ecosystem functions and services provided by such community, there is limited evidence linking both processes on multitrophic systems.

@@

While drivers of temporal stability have been well study in plant communities [@Ruijven2007; @Gross2014; @Craven2018; @Leps2018; @Sasaki2019; @Valencia2020; @Kigel2021], relatively few studies have evaluated how this same drivers can affect community stability in mobile organisms such as pollinators [@Ebeling2008; @Senapathi2021; @Lazaro2022].
A first outcome of our analysis is that asynchrony of species abundances is a key driver of visitation rate stability.
This stability-asynchrony relationship has been found by different theoretical and empirical studies [@DeMazancourt2013; @Bluthgen2016; @Leps2018; @Sasaki2019; @Valencia2020; @Kigel2021].
For example, Lázaro et al.(2022) also found for plants, pollinators and their interactions that more asynchronous communities being more temporal stable.
In this sense, species asynchrony can increase temporal stability of visitation rate when the abundance of one species increases as a result of decreases in the abundance of another species, density compensation (Winfree & Kremen, 2009;Mukherjee et al 2019); or also in response to the same environmental changes, response diversity (Walker et al. 1999; Winfree 2013).[aunque nosotros no sabemos si estos cambios son debido a perturbaciones ambientales, We believe it is important to test the degree to which these stabilizing mechanisms are at work.](Quizas añadir algo asi??)

On the other hand, species richness is considered one of the strongest drivers of community stability in plants (Tilman et al., 2006; Hallett et al., 2014), although Valencia et al. (2020), analyzing a large number of plant community datasets, have reported that this relationship is not as strong.
Pollinator studies, carried out in crop systems, have observed a positive relationship between species richness and stability of floral visits (Ebeling et al 2008) or stability of abundance and richness (Senapathi et al 2021). However, our results show that pollinator richness was positively associated with asynchrony, which might positively affect the stability of visitation rate, but indirectly. Species richness may increase the probability that community contains species with different responses to environmental conditions and perturbations, leading to asynchrony (compensation) among species abundance and thus, to an increase in community stability (Craven et al., 2018; McCann, 2000; Yachi & Loreau, 1999).

Despite the stability is crucial to the sustainability of ecosystem functions, relatively few studies have evaluated the stability of the pollinator visits frequency on pollination services, and those who did used agricultural systems
(Garibaldi et al. 2011, Lázaro and Alomar 2019, Hünicken et al 2021, Bishop et al 2022).The majority of these studies were focused on crops, however, to our knowledge, how the stability of pollinator community affect to the reproductive success of the wild plant community remaining largely unknown.
In pollinator-dependent crops have been observed a greater yield stability with the pollinator diversity and the stability of visitation rate (Garibaldi et al. 2011, Hünicken et al 2021), however in our study system (wild plants), we did not find this relationship.
